Supplementary Materials

### 2023-07-20 manuscript/manuscript.tex
ms updates

With this caveat noted, there are three important but tentative results to draw
from this analysis. First, the estimated mutation rate is implausibly higher,
reaching the upper limit of our optimization boundary of $\mu = 8 \times
10^{-8}$ across all populations in or PhastCons Priority model (Supplementary
Material XXX). Second, all of our leave-one-chromosome-out $R_\text{LOCO}^2$
are about one percentage point higher than the unrescaled model. This improved
fit could be an artifact of the circularity, so it is unimportant. Third, the
DFE estimates for PhastCons regions is now U-shaped, with $75-77\%$ of mass
being placed on a weakly deleterious class, $s=10{^-5}$. Interestingly, this is
the first of all of our models where such an appreciable mass has been placed
on a midpoint in our grid; in all other cases, non-strongly estimates were
neutral ($s=10^{-8}$). Finally, predicted pairwise diversity is nearly
identical to our original, non-locally-rescaled fit (see Supplementary
Materials XXX). This

>>>>

With this caveat noted, there are three important but tentative results to draw
from this analysis. First, the estimated mutation rate is implausibly higher,
reaching the upper limit of our optimization boundary of $\mu = 8 \times
10^{-8}$ across all populations in or PhastCons Priority model (Supplementary
Material XXX). Second, all of our leave-one-chromosome-out $R_\text{LOCO}^2$
are about one percentage point higher than the unrescaled model. This improved
fit could be an artifact of the circularity, so it is unimportant. Third, the
DFE estimates for PhastCons regions is now U-shaped, with $75-77\%$ of mass
being placed on a weakly deleterious class, $s=10{^-5}$. Interestingly, this is
the first of all of our models where such an appreciable mass has been placed
on a midpoint in our grid; in all other cases, non-strongly estimates were
neutral ($s=10^{-8}$). Finally, predicted pairwise diversity is nearly
identical to our original, non-locally-rescaled fit (see Supplementary
Materials Figure \ref{suppfig:rescale}). However, this is not the case when the
locally-rescaled maximum likelihood estimates are used to predict on the
non-locally-rescaled B' maps.

### 2023-07-20 manuscript/supplementary.tex
ms updates

>>>>

\subsection{Locally-Rescaled Fit Results}

\begin{figure}[htbp]
    \label{suppfig:rescale}
  \centering
  \includegraphics[]{figures/supplementary/rescale_pi_pred_plot.pdf}

  \caption{Chromosome 2 predictions on the YRI samples, with locally-rescaled
      model fits. Observed data is the dark gray line, and the normal MLE for
      the PhastCons Priority model is the blue line. The locally-rescaled
      predictions are the green line. The dashed red line are the prediction
      using the standard B' map (without local-rescaled) and the maximum likelihood
      estimates from the locally-rescaled fits. The large discrepancy in this shows
      that estimates are highly dependent on the B' map.}
\end{figure}

\begin{figure}[htbp]
    \label{suppfig:rescale-b}
  \centering
  \includegraphics[]{figures/supplementary/rescale_Bs.pdf}

  \caption{The standard (dark gray) and rescaled (blue) B' maps for different
  $\mu = 1.6 \times 10^{-8}$ and three different selection coefficients. For
$s=10^{-5}$ ($2N_e s = 0.2$), locally-rescaling alters the predicted reduction
so that it is essentially insignificant ($B \approx 1$). }
